On Devon Allen's Disqualification at the 2022 World Track and Field Championships

### 2023-09-06 Manuscript/manuscript.tex
Small changes

Two aims of this section are to determine how extreme a reaction time below
0.1 seconds is, and to determine how the exclusion of 2022 could alter the results.
Using the gamma function with link set to log, the probability of the reaction 
time being less than 0.1 seconds can be calculated in R using the methods 
described in Section~\ref{sec:glmm}. A simulation size of $10,000,000$ was 
chosen to estimate the probability of observing a reaction time below 
two thresholds: 0.1 and 0.08. When including 2022, a probability
of $4.38\cdot10^{-3}$ corresponds to roughly 1 in every 228 starts
being below 0.1 seconds.  When we exclude 2022, the probability of observing a
reaction time below 0.1 seconds decreased to $3.52\cdot10^{-3}$, or 1 in every
285 starts.

@@

\begin{table}
  \centering
  \caption{Probabilities of observing reaction times less than 0.08, 0.09, and
  0.01 seconds based on the two effect model.}
  \begin{tabular}{c c c c} 
   \toprule
   Data Set & P(R. Time $<$ 0.08) & P(R. Time $<$ 0.09) & P(R. Time $<$ 0.1)  \\ 
   \midrule
   Excluding 2022 & $3.19\cdot10^{-5}$ & $4.48\cdot10^{-4}$ &  $3.52\cdot10^{-3}$  \\ 
   Including 2022 & $4.01\cdot10^{-5}$ & $5.82\cdot10^{-4}$ & $4.38\cdot10^{-3}$ \\
   \bottomrule
  \end{tabular}
  \label{tab:Sim_probability}
\end{table}

@@

\begin{table}
  \centering
  \caption{Suggested reaction time barriers based on probability of observing
  a time less than the barrier. \of{Not sure if this makes sense}}
  \begin{tabular}{c c c} 
   \toprule
   Data Set & P(RxnTime $<$ x = $10^{-3}$) & P(RxnTime $<$ x = $10^{-4}$) \\ 
   \midrule
   Old Pooled & $0.093$ & $0.084$ \\ 
   All Pooled & $0.092$ & $0.083$ \\
   \bottomrule
  \end{tabular}
  \label{tab:Sim_time}
\end{table}

>>>>

Two aims of this section are to determine how extreme a reaction time below
0.1 seconds is, and to determine how the exclusion of 2022 could alter the results.
Using the gamma function with link set to log, the probability of the reaction 
time being less than 0.1 seconds can be calculated in R using the methods 
described in Section~\ref{sec:glmm}. A simulation size of $10,000,000$ was 
chosen to estimate the probability of observing a reaction time below 
two thresholds: 0.1 and 0.08. When including 2022, a probability
of $4.34\cdot10^{-3}$ corresponds to roughly 1 in every 230 starts
being below 0.1 seconds.  When we exclude 2022, the probability of observing a
reaction time below 0.1 seconds decreased to $3.54\cdot10^{-3}$, or 1 in every
283 starts.

@@

\begin{table}
  \centering
  \caption{Probabilities of observing reaction times less than 0.08, 0.09, and
  0.01 seconds based on the two effect model.}
  \begin{tabular}{c c c c} 
   \toprule
   Data Set & P(R. Time $<$ 0.08) & P(R. Time $<$ 0.09) & P(R. Time $<$ 0.1)  \\ 
   \midrule
   Excluding 2022 & $3.35\cdot10^{-5}$ & $4.45\cdot10^{-4}$ &  $3.54\cdot10^{-3}$  \\ 
   Including 2022 & $4.20\cdot10^{-5}$ & $5.70\cdot10^{-4}$ & $4.34\cdot10^{-3}$ \\
   \bottomrule
  \end{tabular}
  \label{tab:Sim_probability}
\end{table}

@@

\begin{table}
  \centering
  \caption{Suggested reaction time barriers based on probability of observing
  a time less than the barrier. \of{Not sure if this makes sense}}
  \begin{tabular}{c c c} 
   \toprule
   Data Set & P(RxnTime $<$ x = $10^{-3}$) & P(RxnTime $<$ x = $10^{-4}$) \\ 
   \midrule
   Old Pooled & $0.094$ & $0.084$ \\ 
   All Pooled & $0.092$ & $0.083$ \\
   \bottomrule
  \end{tabular}
  \label{tab:Sim_time}
\end{table}
